\ttitle

### 2015-06-03 Chapters/Introduction.tex
Bibilography file updated

The role of atrial natriuretic peptide (ANP) has also been investigated. Obstructive jaundice is associated with increased levels of ANP as a result of increased cardiac endocrine activity in bile duct ligated rabbits.\parencite{pereira_increased_1994} Similar findings have been reported in humans as well. \parencite{gallardo_increased_1998, martinez-rodenas_circulating_1998)

Moreover, relief of obstructive jaundice is associated with improvement in endocrine markers of fluid homeostasis as well as cardiac function. \parencite{padillo_improved_2001, gallardo_increased_1998) Padillo and co-workers reported that there was a negative correlation between serum bilirubin levels and left ventricular systolic work and this was associated with elevated ANP and BNP (brain natriuretic peptide) levels. However, both ANP and BNP levels decreased after biliary drainage and there was a significant improvement in cardiac output, cardiac index, systolic volume and left ventricular systolic work.\parencite{padillo_improved_2001}

>>>>

The role of atrial natriuretic peptide (ANP) has also been investigated. Obstructive jaundice is associated with increased levels of ANP as a result of increased cardiac endocrine activity in bile duct ligated rabbits.\parencite{pereira_increased_1994} Similar findings have been reported in humans as well. \parencite{gallardo_increased_1998, martinez-rodenas_circulating_1998}

Moreover, relief of obstructive jaundice is associated with improvement in endocrine markers of fluid homeostasis as well as cardiac function. \parencite{padillo_improved_2001, gallardo_increased_1998} Padillo and co-workers reported that there was a negative correlation between serum bilirubin levels and left ventricular systolic work and this was associated with elevated ANP and BNP (brain natriuretic peptide) levels. However, both ANP and BNP levels decreased after biliary drainage and there was a significant improvement in cardiac output, cardiac index, systolic volume and left ventricular systolic work.\parencite{padillo_improved_2001}
